Live Functional Programming with Typed Holes

### 2018-02-28 calculus.tex
note about \dcastthree sugar
Canonical Indeterminate Forms

@@

\begin{theorem}[Canonical Indeterminate Forms]
  \rkc{TODO}

  \rkc{TODO}

  \rkc{TODO}

  \rkc{TODO}

  \rkc{TODO}

  \rkc{TODO}

  \rkc{TODO}

  \rkc{TODO}
\end{theorem}

>>>>

\rkc{this syntactic sugar is used in four places: ITCastSucceed, ITCastFail,
ITGround, and ITExpand. that's not many, and those rules don't look much more
cluttered without the sugar, so consider eliminating it. if so, just toggle the
definition of the dcastthree macro to the unsugared option.}

@@

\begin{theorem}[Canonical Indeterminate Forms]
  If $\hasType{\hDelta}{\emptyset}{\dexp}{\htau}$
  and $\isIndet{\dexp}$
  then either
  \begin{enumerate}[label=(\alph*)]
    \item
      $\dexp=\dehole{u}{\subst}{}$
      and $\Dbinding{u}{\Gamma'}{\htau}\in\hDelta$, or
    \item
      $\dexp=\dhole{\dexp'}{u}{\subst}{}$
      and $\isFinal{\dexp'}$
      and $\hasType{\hDelta}{\emptyset}{\dexp'}{\htau'}$
      and $\Dbinding{u}{\Gamma'}{\htau}\in\hDelta$, or
    \item
      $\dexp=\dap{\dexp_1}{\dexp_2}$
      and $\hasType{\hDelta}{\emptyset}{\dexp_1}{\tarr{\htau_2}{\htau}}$
      and $\hasType{\hDelta}{\emptyset}{\dexp_2}{\htau_2}$
      and $\isIndet{\dexp_1}$
      and $\isFinal{\dexp_2}$
      and $\dexp_1\neq\dcasttwo{\dexp_1}{\tarr{\htau_3}{\htau_4}}
                                        {\tarr{\htau_3'}{\htau_4'}}$, or
    %% \item
    %%   \begin{enumerate}
    %%     \item blah
    %%     \item blah
    %%     \item blah
    %%   \end{enumerate}
    \item
      $\htau=b$
      and $\dexp=\dcasttwo{\dexp'}{\tehole}{b}$
      and $\isIndet{\dexp'}$
      and $\dexp'\neq\dcasttwo{\dexp''}{\htau'}{\tehole}$, or
    \item
      $\htau=b$
      and $\dexp=\dcastfail{\dexp'}{\htau'}{b}$
      and $\isGround{\htau'}$
      and $\htau'\neq{b}$
      and $\hasType{\hDelta}{\emptyset}{\dexp'}{\htau'}$, or
    \item
      $\htau=\tarr{\htau_{11}}{\htau_{12}}$
      and $\dexp=\dcasttwo{\dexp'}{\tarr{\htau_1}{\htau_2}}
                                  {\tarr{\htau_{11}}{\htau_{12}}}$
      and $\isIndet{\dexp'}$
      and $\tarr{\htau_1}{\htau_2}\neq\tarr{\htau_{11}}{\htau_{12}}$, or
    \item
      $\htau=\tarr{\tehole}{\tehole}$
      %% $\htau=\tarr{\htau_{11}}{\htau_{12}}$
      %% and $\htau_{11}=\tehole$
      %% and $\htau_{12}=\tehole$
      and $\dexp=\dcastthree{\dexp'}{\tehole}{\tehole}{\tehole}$
      and $\isIndet{\dexp'}$
      and $\dexp'\neq\dcasttwo{\dexp''}{\htau'}{\tehole}$, or
    \item
      $\htau=\tarr{\tehole}{\tehole}$
      %% $\htau=\tarr{\htau_{11}}{\htau_{12}}$
      %% and $\htau_{11}=\tehole$
      %% and $\htau_{12}=\tehole$
      and $\dexp=\dcastfail{\dexp'}{\htau'}{\tarr{\tehole}{\tehole}}$
      %% and $\dexp=\dcastfail{\dexp'}{\htau'}{\tarr{\htau_{11}}{\htau_{12}}}$
      and $\htau'\neq\htau$
      and $\isGround{\htau'}$
      and $\isIndet{\dexp'}$
      and $\hasType{\hDelta}{\emptyset}{\dexp'}{\htau'}$, or
    \item
      $\htau=\tehole$
      and $\dexp=\dcasttwo{\dexp'}{\htau'}{\tehole}$
      and $\isGround{\htau'}$
      and $\isIndet{\dexp'}$.
  \end{enumerate}
\end{theorem}
